Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

```{r valtiopaivat, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
# Use timeinterval year intervals
dfsel = df0
#dfsel = subset(df0, publication_place == "Stockholm")
#dfsel = subset(df0, publication_place == "Norrköping")
#dfsel = subset(df0, publication_place == "Gävle")

@@

>>>>

```{r valtiopaivat-total, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
# Use timeinterval year intervals
dfsel = df0
#dfsel = subset(df0, publication_place == "Stockholm")
#dfsel = subset(df0, publication_place == "Norrköping")
#dfsel = subset(df0, publication_place == "Gävle")

@@

```{r valtiopaivat-gavle, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
# Use timeinterval year intervals
myplace = "Gävle" # Norrköping / Stockholm
dfsel = subset(df0, publication_place == myplace)

rect_left <- c(min(na.omit(dfm$date)),
               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792	       
               max(na.omit(dfm$date)))
  rectangles <- data.frame(
    xmin = rect_left[-length(rect_left)],
    xmax = rect_left[-1],
    #xmin = min(dfsel$publication_year),
    #xmax = max(dfsel$publication_year),    
    ymin = ymin,
    ymax = ymax
    )
  rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
  #rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))

# Draw Figure
theme_set(theme_bw(20))
p <- ggplot()
p <- p + geom_rect(data = rectangles, 
	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
         scale_fill_manual(values = cols) # + guides(fill = "none") 
p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + scale_x_continuous(breaks=seq(min(dfsel$publication_year), max(dfsel$publication_year), 20))
p <- p + ggtitle("Publishing activity")
p <- p + ylab("Documents / Year")
p <- p + xlab("Year")
p <- p + ggtitle(paste("Riksdagar - titlecount in", myplace, sep = ""))
print(p)
```
